SciUnit: Collaborative Infrastructure for Test-Driven\\Scientific Model Validation

### 2014-03-13 sciunit-icse14/sciunit-icse14.tex
Code updated to match SciUnit

% Section 2.
\section{Validation Testing with {SciUnit}}
\begin{figure}[t]
\small
\begin{python}
class PositionTest(sciunit.Test):
    """Tests a planetary position model based on positions observed on day n given the positions in the n-1 previous days.
    Metric: Standard p-value.
    Parameters: 
      obs_histories : list[list[position]]
      obs_positions: list[position]"""
	def __init__(self, obs_histories, obs_positions):
		self.obs_histories = obs_histories
		self.obs_positions = obs_positions

@@

	def _judge(self, model):
		predictions = []
		for obs_history in self.obs_histories:
			predictions.append(model.predict_next_pos(obs_history))
		p = pooled_p_val(predictions, self.obs_positions)
		return sciunit.PValue(p, related_data={
			'obs_histories': obs_histories,
			'obs_positions': obs_positions,
			'predictions': predictions
		})
\end{python}
\vspace{-5px}
\caption{An example test class in \texttt{cosmounit}.}
\label{fig:rate_test}
\vspace{-15px}
\end{figure}

@@

A \textit{SciUnit} validation test is an {instance} of a Python class implementing the \verbx{sciunit.Test} abstract interface (line 1). 
Here, the class \verbx{PositionTest} takes two \emph{parameters} in its constructor (constructors are named \verbx{\_\_init\_\_} in Python, lines 7-9). 
The meaning of each parameter along with a description of the goodness-of-fit metric used by the test is documented on lines 2-6. 
%For convenience, we also make use of functions provided by the popular NumPy\cite{numpy_url} and SciPy\cite{scipy_url} libraries, although these are not required by \textit{SciUnit}.  
To create a \emph{particular} position test, we instantiate this class with particular planetary observations. 
For example, the subset of cosmologists interested specifically in Saturn might instantiate a test by randomly chunking observations made about Saturn as follows:
\begin{python}
  h, p = randomly_chunk(saturn_obs_positions)
  saturn_position_test = SpikeCountTest(h, p)
\end{python}

@@

Classes that implement the \verbx{sciunit.Test} interface must contain a \verbx{_judge} method that receives a candidate \emph{model} as input and produces a \textit{score} as output. 
To specify the interface between the test and the model, the test author provides a list of \emph{capabilities} in the \verbx{required_capabilities} attribute, seen on line 11 of Fig. \ref{fig:rate_test}. 
Capabilities are simply collections of methods that a test will need to invoke in order to receive relevant data, and are analogous to \emph{interfaces} in e.g. Java. 
In Python, capabilities must be written as classes with unimplemented members. 
The capability required by the test in Figure \ref{fig:rate_test} is shown in Figure \ref{fig:capability}. 
In \textit{SciUnit}, classes defining capabilities are tagged as such by inheriting from \verbx{sciunit.Capability}. The test in Figure \ref{fig:rate_test} repeatedly uses this capability on line 16 to produce a position prediction for each observation.  We assume that positions are represented in a standardized manner specified within \verbx{cosmounit}. A model is simply an object that implements capabilities (via Python's simple inheritance mechanism).

The remainder of the \verbx{_judge} method compares the model predictions to observed data to produce a pooled $p$ value. The method returns an instance of \verbx{sciunit.PValue}, a subclass of \texttt{sciunit.Score} that has been included with \textit{SciUnit} due to its generality. In addition to the $p$-value itself, the returned score object also contains metadata, via the \verbx{related_data} parameter, for  scientists who may wish to examine the result in more detail later. This illustrates some key differences between unit testing, which would simply produce a boolean result, and our conception of scientific validation testing (challenge 1). A score must induce an ordering, so that the table shown in Figure 1 can be sorted along its columns, and it can optionally specify a normalization scheme so the cells can be color-coded (not shown). A test can be manually executed using the \verbx{judge} method:
\begin{python}
score = saturn_position_test.judge(kepler_sat)
\end{python}

This method proceeds by first checking that the provided model implements all required capabilities before calling the test's \verbx{_judge} method to produce a score. A reference to the test and model are added to the score for convenience (accessible via the \verbx{test} and \verbx{model} attributes, respectively).

>>>>

% Section 2.
\section{Validation Testing with {SciUnit}}
\begin{figure}[t]
\small
\begin{python}
class PositionTest(sciunit.Test):
    """Tests a planetary position model based on positions observed on day n given the positions in the n-1 previous days.
    Metric: Standard p-value.
    Parameters: 
      observation : ['histories':histories, 'positions':positions]
        histories : list[list[position]]
        positions : list[position]"""

@@

	def generate_prediction(self, model):
		predictions = []
		for obs_history in self.observation['histories']:
			predictions.append(model.predict_next_pos(obs_history))
		return predictions

	def compute_score(observation, prediction):
		obs_positions = observation['positions']
		p = pooled_p_val(predictions, obs_positions)
		return sciunit.scores.PValue(p, related_data={
			'obs_histories': observation['histories'],
			'obs_positions': obs_positions,
			'predictions': predictions
		})
\end{python}
\vspace{-5px}
\caption{An example test class in \texttt{cosmounit}.}
\label{fig:rate_test}
\vspace{-15px}
\end{figure}

@@

A \textit{SciUnit} validation test is an {instance} of a Python class implementing the \verbx{sciunit.Test} abstract interface (line 1). 
A test takes one required parameter in its constructor (constructors are named \verbx{\_\_init\_\_} in Python, lines 7-9), summarizing observed data against which the test will validate models. 
For the class \verbx{PositionTest}, this observation parameter is a dictionary containing two kinds of observations.   
The meaning of this parameter along with a description of the goodness-of-fit metric used by the test is documented on lines 2-6. 
%For convenience, we also make use of functions provided by the popular NumPy\cite{numpy_url} and SciPy\cite{scipy_url} libraries, although these are not required by \textit{SciUnit}.  
To create a \emph{particular} position test, we instantiate this class with particular planetary observations. 
For example, the subset of cosmologists interested specifically in Saturn might instantiate a test by randomly chunking observations made about Saturn as follows:
\begin{python}
  h, p = randomly_chunk(saturn_obs_positions)
  saturn_position_test = SpikeCountTest({'histories':h, 'positions':p)
\end{python}

@@

Classes that implement the \verbx{sciunit.Test} interface must contain a \verbx{generate_prediction} method that receives a candidate \emph{model} as input and produces a prediction as output. 
They must also contain a \verbx{compute_score} method that can take this prediction, and the observation used to instantiate the test, and produce a \verbx{score}.  
To specify the interface between the test and the model, the test author provides a list of \emph{capabilities} in the \verbx{required_capabilities} attribute, seen on line 11 of Fig. \ref{fig:rate_test}. 
Capabilities are simply collections of methods that a test will need to invoke in order to receive relevant data, and are analogous to \emph{interfaces} in e.g. Java. 
In Python, capabilities must be written as classes with unimplemented members. 
The capability required by the test in Figure \ref{fig:rate_test} is shown in Figure \ref{fig:capability}. 
In \textit{SciUnit}, classes defining capabilities are tagged as such by inheriting from \verbx{sciunit.Capability}. The test in Figure \ref{fig:rate_test} repeatedly uses this capability on line 16 to produce a position prediction for each observation.  We assume that positions are represented in a standardized manner specified within \verbx{cosmounit}. A model is simply an object that implements capabilities (via Python's simple inheritance mechanism).

The remainder of the \verbx{compute_score} method compares the model predictions to observed data to produce a pooled $p$ value. The method returns an instance of \verbx{sciunit.scores.PValue}, a subclass of \texttt{sciunit.Score} that has been included with \textit{SciUnit} due to its generality. In addition to the $p$-value itself, the returned score object also contains metadata, via the \verbx{related_data} parameter, for  scientists who may wish to examine the result in more detail later. This illustrates some key differences between unit testing, which would simply produce a boolean result, and our conception of scientific validation testing (challenge 1). A score must induce an ordering, so that the table shown in Figure 1 can be sorted along its columns, and it can optionally specify a normalization scheme so the cells can be color-coded (not shown). A test can be manually executed using the \verbx{judge} method:
\begin{python}
score = saturn_position_test.judge(kepler_sat)
\end{python}

This method proceeds by first checking that the provided model implements all required capabilities before calling the test's \verbx{compute_score} method to produce a score. A reference to the test and model are added to the score for convenience (accessible via the \verbx{test} and \verbx{model} attributes, respectively).
